\vfill A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-05-16 Paper/paper.tex
Evaluation edits

\subsection{PolyXpress (PX)\cite{PX}}
Our major evaluation application was an in-house application called PolyXpress (PX). As the About page says, ``PolyXpress allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.'' Users can play or create ``Stories'', each of which consists of ``Chapters''. Each chapter consists of various ``Events''. Each ``Event'' generally give the user some sort of information, in the form of text, video, audio, or a picture. After the player has chosen a story, they must physically reach certain checkpoints to unlock chapters and events. Because the application requires physical movement, it works solely on devices with GPS, generally phones and tablets only. Rather than put a series of pictures showing PolyXpress here, we will put them in the appendix at the end of the paper. To get a better sense of what PolyXpress does and looks like, we recommend looking at the appendix now.

PolyXpress consists of three smaller application: 1) The Player. 2) The Author. 3) The PointKBFinder.

@@

The goal of a unit test, is to test the function, module, ``unit'' in isolation. While that sounds great in theory, things tend to get messier when it comes to the actual code. The method we used to alleviate this issue was with mock functions and objects. Mocks are stand-in pieces of code that get called instead of the real implementation. Mocks are highly controlled and often just simply return the same value regardless of parameters or prior calls.

>>>>

\subsection{PolyXpress (PX)\cite{PX}}
Our major evaluation application was an in-house application called PolyXpress (PX). As the About page says, ``PolyXpress allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.''\cite{PX} Users can play or create ``Stories'', each of which consists of ``Chapters''. Each chapter consists of various ``Events''. Each ``Event'' generally give the user some sort of information, in the form of text, video, audio, or a picture. After the player has chosen a story, they must physically reach certain checkpoints to unlock chapters and events. Because the application requires physical movement, it works solely on devices with GPS, generally phones and tablets. Rather than put a series of pictures showing PolyXpress here, we will put them in the appendix at the end of the paper. To get a better sense of what PolyXpress does and looks like, we recommend looking at the appendix now.

PolyXpress consists of three smaller application: 1) The Player. 2) The Author. 3) The PointFinder.

@@

The goal of a unit test, is to test the function, module, or ``unit'' in isolation. While this sounds great in theory, things tend to get messier when it comes to the actual code. The method we used to alleviate this issue was to create mock functions and objects. Mocks are stand-in pieces of code that get called instead of the real implementation. Mocks are highly controlled and often just simply return the same value regardless of parameters or prior calls. Mock functions are just as their name implies, a function with a known return value regardless of parameters that is named the same things as what the unit is calling. Mock objects are objects with attributes and functions that the unit interacts with instead of the real object it will interact with in production.
